Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-10-23 RNARedPrint.tex
sync from overleaf

\author[
    addressref={aff1,aff2,aff3},
    email={stefan.hammer@uni-leipzig.de}
]{\inits{SH} \fnm{Stefan} \snm{Hammer}}
%
\author[
    addressref={aff4},
    email={wei.wang@lix.polytechnique.fr}
]{\inits{WW} \fnm{Wei} \snm{Wang}}
%
\author[
    addressref={aff2,aff3},
    email={will@tbi.univie.ac.at}
]{\inits{SW} \fnm{Sebastian} \snm{Will$^*$}}
%
\author[
    addressref={aff4,aff5},
    corref={aff4},                       % id of corresponding address, if any
    email={yann.ponty@lix.polytechnique.fr}
]{\inits{YP} \fnm{Yann} \snm{Ponty}}

@@

% $^{\text{\sf 5}}$ AMIBio team, Inria Saclay, Bat Alan Turing, 91120 Palaiseau, France}
\address[id=aff5]{%
    \orgname{AMIBio team, Inria Saclay},
    \street{Bat. Alan Turing},
    \postcode{91120}
    \city{Palaiseau},
    \cny{France}
}

@@

Moreover, we provide a {\tt Python} wrapper script that targets prescribed energies using multi-dimensional Boltzmann sampling.
For a given set of secondary structures, together with prescribed target energies
and target \GCb\%, this script generates a series of sequences that satisfy the target values for the energy and
\GCb\% features within configurable tolerances.
Notably, these target energies are actual free energies in the realistic
Turner energy model, and are targeted by efficiently sampling in the
base pair energy model, and filtering sequences based on the {\tt RNAeval} tool from the Vienna package~\cite{Lorenz2011}.

@@

{Stefan: \em Mention RNAsketch to perspectives for more complex design scenario + need for generic constraints-based framework for flexibility ($\to$ generic constraint framework).}

@@

\section*{Author's contributions}
  YP and SW initiated the project and worked out the algorithms.
  % SW---I guess we don't need to be super-detailed, otherwise something like...
  %YP contributed the multi-dimensional Boltzmann sampling background and the \#P-hardness proof.
  %SW contributed the integration with the constraint network setting and its specialization to RNA design.
  YP and WW wrote the core software, while SW and SH contributed additional scripts. SH devised and conducted the computational experiments. All authors wrote, read, and approved the manuscript.
    % Text for this section \ldots
    % https://www.biomedcentral.com/getpublished/editorial-policies#authorship

>>>>

\author[
    addressref={aff1,aff2,aff3},
    email={stefan.hammer@uni-leipzig.de}
]{\inits{SH} \fnm{Stefan} \snm{Hammer}}
%
\author[
    addressref={aff4},
    email={wei.wang@lix.polytechnique.fr}
]{\inits{WW} \fnm{Wei} \snm{Wang}}
%
\author[
    addressref={aff2,aff3},
    email={will@tbi.univie.ac.at}
]{\inits{SW} \fnm{Sebastian} \snm{Will$^*$}}
%
\author[
    addressref={aff4},
    corref={aff2,aff4},                       % id of corresponding address, if any
    email={will@tbi.univie.ac.at; yann.ponty@lix.polytechnique.fr}
]{\inits{YP} \fnm{Yann} \snm{Ponty}}

@@

% $^{\text{\sf 5}}$ AMIBio team, Inria Saclay, Bat Alan Turing, 91120 Palaiseau, France}

@@

Moreover, we provide two {\tt Python} wrapper scripts. The first script targets prescribed energies using multi-dimensional Boltzmann sampling.
For a given set of secondary structures, together with prescribed target energies
and target \GCb\%, this script generates a series of sequences that satisfy the target values for the energy and
\GCb\% features within configurable tolerances.
Notably, these target energies are actual free energies in the realistic
Turner energy model, and are targeted by efficiently sampling in the
base pair energy model, and filtering sequences based on the {\tt RNAeval} tool from the Vienna package~\cite{Lorenz2011}. The second script generates high quality seed sequences suitable for negative RNA design. The details of this approach are described in the subsections below.

@@

@@

\section*{Author's contributions}
  YP and SW initiated the project and designed the algorithms.
  % SW---I guess we don't need to be super-detailed, otherwise something like...
  %YP contributed the multi-dimensional Boltzmann sampling background and the \#P-hardness proof.
  %SW contributed the integration with the constraint network setting and its specialization to RNA design.
  YP, SW and WW wrote the core software, while SW and SH contributed the weight optimization scripts. SH, SW and YP devised the computational experiments, which were conducted by SH. All authors wrote, read, and approved the manuscript.
    % Text for this section \ldots
    % https://www.biomedcentral.com/getpublished/editorial-policies#authorship
